\section{Work Plan}

\subsection{Now - June 2013}
  Since I will be pre-occupied with exams, I find it unlikely that any significant progress will be made on further implementation in this time-frame. It is possible that several spontaneous ideas that could shape the direction of the project may be recorded but no coding is planned.

\subsection{June 2013 - July 2013}
In the first month of summer without revision taking up free time, I hope to finalize my work on the purely Functional Programming aspect of the framework that has been completed so far. This includes the time taken to gather metrics and optimise any discovered bottlenecks that are reducing the performance of the system. At this point I am to have the functional library in a state where I would be happy releasing it if it were the sole result of this project.

\subsection{July 2013 - September 2013}
Over the later part of summer, significant progress should be made in the MapReduce aspect of the framework. Behavioural tests for the sequential work-flow examples should be completed early on and the underlying implementation details should be decided for the MapReduce engine.

The more work done in this period, the less busy the 5th year semesters will be --- so large amounts of work will be advantageous in reducing the work-pressure later on.

\subsection{Semester 1}
Depending on previous progress with the framework, missing features and loose ends should be tied up in this time-period. Time should be taken to profile and optimise the implementation and to provide report material about which back-end decisions were taken and why. By the end of this semester, all coding on the project should be completed so that the final semester can focus solely on report writing and gathering any missing data about performance without concentrating on rewriting the codebase.
\subsection{Semester 2}
Some time shall be spent convincing fellow students to attempt to use the framework for their personal projects and recording information about how successful these endeavours are.
Remaining time will be spend writing documentation and the final report for the dissertation. No code modification should be necessary during this period.

If serious problems are encountered at any point during the previous semester's progress towards the framework, the first four weeks of semester 2 may be used as an emergency catch-up buffer. However this is not part of the plan and if work continues at the planned pace this will not be necessary.
