\section{Evaluation}
\subsection{Performance}
In order to understand how my implementation performs against alternatives, both as I iteratively improve it and when I intend to release it, I shall be providing results of various performance tests.

For each feature present, my framework will be compared against existing projects or language constructs that provide such functionality. When demonstrating a functional Map implementation, I may detail the time taken for a language's default Map implementation alongside the results of my library performing on both the GPU and CPU as compute devices.

I hope to enhance such comparisons by providing granulated details of the time taken for various stages of execution, in order to highlight which aspects scale well to GPU environments and which do not.

In addition to 'artificial' benchmarks that show how individual actions perform, I hope to produce several equivalent code samples using competing methodologies and perhaps show that the entire process of performing some task, such as machine-learning, can be performed quicker when including my framework into an existing high-level implementation without sacrificing clarity.
\subsection{Usability}
Since I do not wish to significantly reduce the usability of my outcome simply to provide the highest performance possible, I shall be conducting several user-evaluation trials in order to influence my design decisions.

I will observe real-world users applying functions that I will develop to requirements of personal projects or experimental scenarios. I will record which aspects of the provided framework they find issues with and investigate whether anything can be improved in these cases.

I will also attempt to package my resultant framework in a way that makes it simple to obtain and include into projects by interested parties.
\subsection{Portability}
In addition to ensuring that the project is simple to obtain and utilise, I will be testing it on as many compatible build environments and hardware architectures as possible to demonstrate its suitability as a general solution.
