\section{Output and Work Plan}
\subsection{Immediate Focus - Spring 2013}
The first stage of implementation is to produce an underlying library for higher-order functiontional programming tasks.
By making it simpler to enqueue OpenCL kernels and get datasets to/from the device, this will enable easy evaluation of necessary scheduling techniques.

Once the library has implemented higher-order functions for basic data types, an initial comparison of its advantages against existing methods shall be produced.

At this point a test-suite with high code-coverage shall be built in order to provide strong assertions that given substitutions to existing methods are correct.
\subsection{Later Focus - Late Spring/Summer 2013}
A series of implementation possibilities shall be considered after greater evaluation of existing relevant MapReduce frameworks. After shortlisting areas of interest and constructing novel methods to investigate, a modular system shall be constructed whereby combinations of concepts resultant from these decisions can be tested.
\subsection{Prior to Release - Winter 2013}
After functional completeness, the focus of the project is pareto-efficient optimisation of performance, usability and portability without degrading the correctness or capabilities of the system.
\subsection{Final Output of Implementation - Early 2014}
The framework will be released with features explained in this proposal alongside relevant documentation.

The project's source should be released, with a suitably clean code-structure, to encourage further experimentation and allow investigation of techniques developed during the lifetime of this project.

\subsection{Dissertation - Remaining Time}
The research undertaken throughout this project will be presented in a report documenting the problems faced and solved by the choices made. Evaluations of the project's performance against competing platforms shall be presented in detail alongside conclusions drawn.
